Standard Candle Cosmology With Incomplete Spectroscopic Classification

### 2015-11-12 doc/article.tex
test of slack
test des-sn slack
get rid of absolute paths in document.
Fix flux calculation as sncosmo source normalization is based
of f, not f_lambda

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=6.5in]{/Users/akim/project/abc/results/hdpgm.pdf} 
   \caption{Probabilistic Graphical Model for the SN~Ia analysis.  
   The description of the elements and dependencies of the model are given in
   \S\ref{model:sec}.
   \label{pgm:fig}}
\end{figure}

@@

@@

@@

\bibliographystyle{elsarticle-num} 
\bibliography{/Users/akim/Documents/alex}

>>>>

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=6.5in]{../results/hdpgm.pdf} 
   \caption{Probabilistic Graphical Model for the SN~Ia analysis.  
   The description of the elements and dependencies of the model are given in
   \S\ref{model:sec}.
   \label{pgm:fig}}
\end{figure}

@@

\section{Design}
\subsection{Data}
There is photometry, redshift, host properties, type/subtype.  The pdf's of redshift and
host-properties may be more complicated than a normal distribution due to uncertain host
determination and photometric redshifts.  The photometry is expected to be a Gaussian
with a full covariance matrix due to the host-galaxy subtraction.

@@

Danny writes everything!

@@

\bibliographystyle{elsarticle-num} 
\bibliography{alex}
